Rough calculations

### 2015-11-01 notes/rough-calculations.Rmd
.

    ```{r space_recomb, cache=TRUE}
    s <- 0.01
    rvals <- exp(seq(log(1e-3),log(0.5),length.out=20))
    tt <- seq(0,200,length.out=10)
    thegrid <- setup.grid.1D(x.up=-100, x.down=100, N = 5000)
    fwds.soln <- forwards_pde(s=s,times=seq(0,1.2*max(tt),length.out=1000),grid=thegrid)
    r.solns <- lapply(rvals, function(r) {
            forwards_backwards_pde(s=s,times=tt,grid=thegrid,r=r,log.p=TRUE,fwds.soln=fwds.soln)
        } )
    unlinked.clines  <- lapply(r.solns, cline_from_soln, grid=thegrid )
    xr <- lapply( seq_along(tt), function (k) { do.call( cbind, lapply( unlinked.clines, function (x) x[k,-1] ) ) } )
    ```
    ```{r plot_sr}
    for (k in 2:length(xr)) {
        matplot(thegrid$x.mid, xr[[k]], type='l', col=rainbow(2*length(rvals)), lty=1, main=sprintf("t=%f",tt[k]) )
        legend("bottomright",lty=1, col=rainbow(2*length(rvals)), legend=sprintf("r=%f : %f",rvals,rvals*sqrt(tt[k]/2/s)))
    }
    ```

>>>>

    ```{r space_recomb, cache=TRUE}
    s <- 0.01
    rvals <- exp(seq(log(1e-3),log(0.5),length.out=20))
    tt <- seq(0,200,length.out=10)
    thegrid <- setup.grid.1D(x.up=-100, x.down=100, N = 5000)
    fwds.soln <- forwards_pde(s=s,times=seq(0,1.2*max(tt),length.out=1000),grid=thegrid)
    r.solns <- lapply(rvals, function(r) {
            forwards_backwards_pde(s=s,times=tt,grid=thegrid,r=r,log.p=TRUE,fwds.soln=fwds.soln)
        } )
    unlinked.clines  <- lapply(r.solns, cline_from_soln, grid=thegrid )
    xr <- lapply( seq_along(tt), function (k) { do.call( cbind, lapply( unlinked.clines, function (x) x[k,-1] ) ) } )
    ```
    ```{r plot_sr}
    for (k in 2:length(xr)) {
        matplot(thegrid$x.mid, xr[[k]], type='l', col=rainbow(2*length(rvals)), lty=1, main=sprintf("t=%f",tt[k]), ylab='probability' )
        legend("bottomright",lty=1, col=rainbow(2*length(rvals)), legend=sprintf("r=%f : %f",rvals,rvals*sqrt(tt[k]/2/s)),cex=0.5)
    }
    ```
